Patchwork: Incremental Computation for Abstract Interpretation

### 2019-02-25 paper.tex
Flesh out contributions, add REVISER section

\begin{enumerate}
    \item We propose an efficient incremental naming strategy for the worklist algorithm over a CFG.
    \item We provide an incremental abstract interpretation framework which can express any domain of interest. (Wording? Any domain + widening operator? Point is frees the monotonicity restriction)
    \item We demonstrate that our framework is competitive, performance-wise, with 'Datalog-style' alternatives.
\end{enumerate}

@@

\begin{enumerate}
    \item Does Patchwork achieve significant performance gains on incremental edits relative to a non-incremental baseline tool? (check overhead/speedup constants)
    \item Is Patchwork competitive with alternative tools for incremental static analysis (IncA)? (direct comparison on parity analysis)
    \item Is the added expressivity of Patchwork relevant to clients? (check false alarm rates on impoverished interval analysis v. regular)
\end{enumerate}

@@

@@

%% Appendix
\appendix
\section{Appendix: Datalog Strategy - Limitations + Comparison}

>>>>

\begin{enumerate}
    \item We propose an efficient incremental naming strategy for the worklist algorithm over a CFG.\\
    Using Adapton requires a strategy for uniquely naming subcomputations inside an algorithm. The goal is to ensure that after a minor edit, identical subcomputations have the same name across runs, so that Adapton can re-use work from a prior run. We present a naming strategy which names the transfer function at each CFG node by the program location and current abstract state. We demonstrate that this achieves significant re-use across runs in the presence of typical small edits to a program.
    \item We provide an incremental abstract interpretation framework which can express any domain of interest.\\
    Patchwork allows clients to use our naming strategy for arbitrary abstract domains. The user must supply a language specification and an implementation of the desired transfer function. With this supplied, Patchwork runs the analysis and can execute incremental runs. We demonstrate the use of Patchwork on several numerical domains - parity and interval - but non-numerical domains can be used as well. There are no restrictions on the domains or transfer functions supplied by the user, an improvement over alternatives which require all operators to be monotonic.
    \item We demonstrate that our framework is competitive, performance-wise, with 'Datalog-style' alternatives.\\
\end{enumerate}

@@

\begin{enumerate}
    \item Does Patchwork achieve significant performance gains on incremental edits relative to a non-incremental baseline tool? (check overhead/speedup constants)
    \item Is the added expressivity of Patchwork relevant to clients? (check false alarm rates on impoverished interval analysis v. regular)
    \item Is Patchwork competitive with alternative tools for incremental static analysis (IncA)? (direct comparison on parity analysis)
\end{enumerate}

@@

Reviser: Reviser is similar to Patchwork in that it tracks the graph structure of static analyses to achieve incremental performance games. Reviser uses the IDFS framework, which builds an exploded CFG tracking both control flow and abstract state dependencies in the program. Like Adapton, Reviser identifies portions of the computation changed by an edit and only 'cleans' the graph edges reachable from the edited regions. However, Reviser is tightly coupled with the IDFS framework, and cannot express more general graph-based computations. Moreover, the performance gains from Reviser are entirely from re-computing over a subset of the original graph - the creators indicate that their clean/repropogate algorithm is \textit{slower} than an initial run - as opposed to Adapton's ability to cache and re-use memoized data.

@@

\newpage
%% Appendix
\appendix
\section{Appendix: Datalog Strategy - Limitations + Comparison}
